HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
more about iaa

@@

\begin{figure*}
  \begin{adjustbox}{trim=2.3cm 0 0 0}
  \begin{tikzpicture}
    [level 1/.style={sibling distance=7.5em},
      level 2/.style={sibling distance=5em},
      level 3/.style={sibling distance=5em},
      level 4/.style={sibling distance=3em}]
    %[semithick, x=2.4cm,y=0.8cm, >=latex, baseline=7ex,
    %  inner sep=.3ex, outer sep=.7ex, minimum size=1.2ex,->]
  \node (ROOT) [label={B}] [fill=blue, circle] {}
  child {node (H3) [label={A}] [fill=yellow,circle] {}
    child {node [label={[red]:R}] {Golf} edge from parent node[left] {}}
    child {node (H1) [label={[orange]30:O}] [fill=orange,circle] {}
      child {node [label={}] {became} edge from parent node[left]  {}}
      child {node [label={}] {a} edge from parent node[left]  {}}
      child {node [label={}] {passion} edge from parent node[left]  {}}
    }
    child {node (H2) [label={A}] [fill=yellow,circle] {}
      child {node {} edge from parent[draw=none] {}}
      child {node {} edge from parent[draw=none] {}}
      child {node {} edge from parent[draw=none] {}}
      child {node {} edge from parent[draw=none] {}}
      child {node [label={[red]:R}] {for} edge from parent node[left]  {}}
      child {node [label={[green]:G}] {his} edge from parent node[left]  {}}
      child {node [label={[orange]:O}] {oldest} edge from parent node[left]  {}}
      child {node [label={[green]:G}] {daughter} edge from parent node[left]  {}}
    }
  }
  child {node {} edge from parent[draw=none] {}}
  child {node (H4) [label={[]30:A}] [fill=yellow,circle] {}
    child {node (she) [label={[green]:G}] {she} edge from parent node[left]  {}}
    child {node [label={[green]:G}] {attended} edge from parent node[left]  {}}
    child {node [label={[green]:G}] {daily} edge from parent node[left]  {}}
    child {node [label={[green]:G}] {lessons} edge from parent node[left]  {}}
  }
  child {node [label={[red]:R}] {and} edge from parent node[left]  {}}
  child {node (H5) [label={A}] [fill=yellow,circle] {}  
    child {node [label={[red]:R}] {greatly} edge from parent node[left] {}}
    child {node [label={[orange]:O}] {improved} edge from parent node[left] {}}
  };
  \draw[dashed] (H5) -> (she) ;

  \com{
  child {node (H1) [label={\#8}] [fill=black,circle] {}
    child {node [label={\#2}] {graduation} edge from parent node[right] {$P$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    }
    child {node (H2) [label={\#9}] [fill=black,circle] {}
      child {node  {} edge from parent[draw=none]}
      child {node  {} edge from parent[draw=none]}
      child {node [label={\#3}] (Tom) {Tom} edge from parent node[right] {$A$}}
      child {node [label={\#4}] {moved} edge from parent node[right] {$P$}}
      child {node [label={\#10}] [fill=black,circle] {}
        child {node [label={\#5}] {to} edge from parent node[right] {$R$}}
        child {node [label={\#6}] {NYC} edge from parent node[right] {$C$}}
        edge from parent node[right] {$A$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    };
    \draw (H1) -> (Tom) node[midway, right] {$A$ \hspace{0.2cm}};
    }
  \end{tikzpicture}
  \end{adjustbox}
\caption{\label{fig:ucca_example2}
  Sample UCCA annotation. Edge labels mark UCCA categories. \#$<$index$>$ marks the node
indices.}
\end{figure*}

@@

To calculate Kappa, we consider the annotation task as a classification task on 
nodes, and consider all nodes where there are two annotations from different
annotators \XXX{unfinished sentence?}
We report the overall Kappa, as well as separate Kappas on lexical
nodes (annotated as red, orange or green) and the structural nodes (annotated
as acceptable or bad). In general there should not be confusion between the two
types of nodes, and in future work the separation between the nodes should be enforced
by the tool.  The Kappas are shown in \tabref{tab:iaa}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & 181 & 102 & 334 & 217 \\
\hline
All nodes & 4686   & 2793   & 8384   & 5604  \\
Kappa & 0.64   & 0.61   & 0.58   & 0.69  \\
\hline
Lexical nodes & 2982 & 1724 & 5386 & 3570 \\
Kappa & 0.54 & 0.29 & 0.54 & 0.50 \\
\hline
Structural nodes & 1602 & 1040 & 2655 & 1989 \\
Kappa & 0.31 & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
\end{center}
\end{table}

To assess whether, as we hoped, HUME would make it easier to reliably annotate long sentences,
we binned the sentences according to length and measured Kappa on each of the bins. Each bin covers
a length range of 10, and we show the variance of kappa with length in \figref{fig:iaalength}.
\XXX{We need to report the number of sentences in each bin, the last German bin
seems to be an unstable result.}

@@

}
\end{tabular}
\caption{Inter-annotator Agreement (Kappa) versus sentence length, separately for
structural and lexical nodes. }
\label{fig:iaalength}

\end{figure*}

\subsection{Discussion of Disagreements}\label{sec:disagreements}

\subsection{Comparison with Crowdsourced Adequacy Judgements}\label{sec:adequacy}

>>>>

\listfiles

@@

\begin{figure*}
  \begin{adjustbox}{trim=2.3cm 0 0 0}
%BH: Not compiling for me, commented out
%  \begin{tikzpicture}
%    [level 1/.style={sibling distance=7.5em},
%      level 2/.style={sibling distance=5em},
%      level 3/.style={sibling distance=5em},
%      level 4/.style={sibling distance=3em}]
%    %[semithick, x=2.4cm,y=0.8cm, >=latex, baseline=7ex,
%    %  inner sep=.3ex, outer sep=.7ex, minimum size=1.2ex,->]
%  \node (ROOT) [label={B}] [fill=blue, circle] {}
%  child {node (H3) [label={A}] [fill=yellow,circle] {}
%    child {node [label={[red]:R}] {Golf} edge from parent node[left] {}}
%    child {node (H1) [label={[orange]30:O}] [fill=orange,circle] {}
%      child {node [label={}] {became} edge from parent node[left]  {}}
%      child {node [label={}] {a} edge from parent node[left]  {}}
%      child {node [label={}] {passion} edge from parent node[left]  {}}
%    }
%    child {node (H2) [label={A}] [fill=yellow,circle] {}
%      child {node {} edge from parent[draw=none] {}}
%      child {node {} edge from parent[draw=none] {}}
%      child {node {} edge from parent[draw=none] {}}
%      child {node {} edge from parent[draw=none] {}}
%      child {node [label={[red]:R}] {for} edge from parent node[left]  {}}
%      child {node [label={[green]:G}] {his} edge from parent node[left]  {}}
%      child {node [label={[orange]:O}] {oldest} edge from parent node[left]  {}}
%      child {node [label={[green]:G}] {daughter} edge from parent node[left]  {}}
%    }
%  }
%  child {node {} edge from parent[draw=none] {}}
%  child {node (H4) [label={[]30:A}] [fill=yellow,circle] {}
%    child {node (she) [label={[green]:G}] {she} edge from parent node[left]  {}}
%    child {node [label={[green]:G}] {attended} edge from parent node[left]  {}}
%    child {node [label={[green]:G}] {daily} edge from parent node[left]  {}}
%    child {node [label={[green]:G}] {lessons} edge from parent node[left]  {}}
%  }
%  child {node [label={[red]:R}] {and} edge from parent node[left]  {}}
%  child {node (H5) [label={A}] [fill=yellow,circle] {}  
%    child {node [label={[red]:R}] {greatly} edge from parent node[left] {}}
%    child {node [label={[orange]:O}] {improved} edge from parent node[left] {}}
%  };
%  \draw[dashed] (H5) -> (she) ;
%
%  \com{
%  child {node (H1) [label={\#8}] [fill=black,circle] {}
%    child {node [label={\#2}] {graduation} edge from parent node[right] {$P$}}
%      %child {node {to Paris} edge from parent node[right] {$A$}}
%      edge from parent node[left] {$H$}
%    }
%    child {node (H2) [label={\#9}] [fill=black,circle] {}
%      child {node  {} edge from parent[draw=none]}
%      child {node  {} edge from parent[draw=none]}
%      child {node [label={\#3}] (Tom) {Tom} edge from parent node[right] {$A$}}
%      child {node [label={\#4}] {moved} edge from parent node[right] {$P$}}
%      child {node [label={\#10}] [fill=black,circle] {}
%        child {node [label={\#5}] {to} edge from parent node[right] {$R$}}
%        child {node [label={\#6}] {NYC} edge from parent node[right] {$C$}}
%        edge from parent node[right] {$A$}}
%      %child {node {to Paris} edge from parent node[right] {$A$}}
%      edge from parent node[left] {$H$}
%    };
%    \draw (H1) -> (Tom) node[midway, right] {$A$ \hspace{0.2cm}};
%    }
%  \end{tikzpicture}
  \end{adjustbox}
\caption{\label{fig:ucca_example2}
  Sample UCCA annotation. Edge labels mark UCCA categories. \#$<$index$>$ marks the node
indices.}
\end{figure*}

@@

To calculate Kappa, we consider the annotation task as a classification task on 
nodes, and consider those nodes which have two annotations from different
annotators.
We report the overall Kappa, as well as separate Kappas on lexical
nodes (annotated as red, orange or green) and the structural nodes (annotated
as acceptable or bad). In general there should not be confusion between the two
types of nodes, and in future work the separation between the nodes should be enforced
by the tool.  The Kappas are shown in \tabref{tab:iaa}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & 181 & 102 & 334 & 217 \\
\hline
All nodes & 4686   & 2793   & 8384   & 5604  \\
Kappa & 0.64   & 0.61   & 0.58   & 0.69  \\
\hline
Lexical nodes & 2982 & 1724 & 5386 & 3570 \\
Kappa & 0.54 & 0.29 & 0.54 & 0.50 \\
\hline
Structural nodes & 1602 & 1040 & 2655 & 1989 \\
Kappa & 0.31 & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
\end{center}
\end{table}

To assess whether, as we hoped, HUME would make it easier to reliably annotate long sentences,
we binned the sentences according to length and measured Kappa on each of the bins. Each bin covers
a length range of 10, and we show the variance of kappa with length in \figref{fig:iaalength}.

@@

}
\end{tabular}
\caption{Inter-annotator Agreement (Kappa) versus sentence length, separately for
structural and lexical nodes. The numbers are the node counts in each bin. }
\label{fig:iaalength}
\end{figure*}

We see from \figref{fig:iaalength} that there is no reduction of IAA with sentence
length, except perhaps in German. Also, from \tabref{tab:iaa} the overall IAA
is quite similar (0.6-0.7) for all languages, showing good agreement, but there are
differences observed when we break down by node type.  In particular, we see a contrast  between
Czech and Polish (where the IAA is higher for lexical nodes than structural nodes) and German and Romanian
(where the reverse  is true). We also observe low IAA (around 0.3) in some cases, for instance 
in German lexical nodes, and for Polish and Czech structural nodes.

\XXX{Discussion of the disagreements}

%\subsection{Discussion of Disagreements}\label{sec:disagreements}

%\subsection{Comparison with Crowdsourced Adequacy Judgements}\label{sec:adequacy}
